Limits to detection of early warning signals: Appendices

### 2012-02-16 appendix/appendices_knit_.Rnw
minor edits and touchups

%% Looks like a comment but it isn't! This is setting the default behavior for the Sweave chunk options, <<options >>= 
% \SweaveOpts{fig.width=7, fig.height=6, fig.align=center, message=FALSE, warning=FALSE}

@@

Simulate from a system approaching a collapse~\Sexpr{nreps} times,

@@

\begin{figure}[H]
\begin{center}
<<crashacor>>=
ggplot(acorr) + geom_line(aes(time, value)) + facet_wrap(~reps) + 
  opts(title="Autocorrelation on replicates from a system approaching a crash")
@
\caption{The pattern of autocorrelation in replicate simulations from a simulation of a system which is approaching a saddle node bifurcation.}\label{crashacor}
\end{center}
\end{figure}

@@

\begin{figure}[H]
<<beanplot>>=
require(beanplot)
beanplot(value ~ simulation, lr, what=c(0,1,0,0))
abline(h=observed, lty=2)
@
\end{figure}

@@

\subsection{Visualizing the simulation replicates}

The \texttt{reps} list also contains the simulation data from each replicate

\begin{figure}[H]
<<<repsplot, fig.width=10>>=
sims <- get_replicates(reps)
ggplot(sims) + geom_line(aes(time, value, group=rep), alpha=0.1) + facet_wrap(~model)
@
\end{figure}

@@

<<moresims>>=
reps <- 500
Asim <- simulate(A, reps)
Bsim <- simulate(B, reps)
@

@@

And gather and plot the distributions,
\begin{figure}[H]
<<tidybean>>=
tidy <- melt(data.frame(null=wsA$tau, test=wsB$tau))
names(tidy) <- c("simulation", "value")
beanplot(value ~ simulation, tidy, what=c(0,1,0,0))
abline(h=observed, lty=2)
@
\end{figure}

@@

Lastly we save the data from each of these examples, that it may be available to the users later.   
<<saveall>>=
save(list=ls(), file="tutorial.rda")
@

>>>>

%% Looks like a comment but it isn't! This is setting the default behavior for the Sweave chunk options, <<options >>= 
% \SweaveOpts{fig.width=4, fig.height=4, fig.align=center, message=FALSE, warning=FALSE, tidy=FALSE, cache=TRUE}

@@

Simulate from a system approaching a collapse~\Sexpr{nreps} times using our population dynamics package, available at \href{https://github.com/cboettig/populationdynamics}{https://github.com/cboettig/populationdynamics},

@@

\setkeys{Gin}{width=0.95\textwidth}

\begin{figure}[H]
\begin{center}
<<crashacor, fig.width=7, fig.height=7>>=
ggplot(acorr) + geom_line(aes(time, value)) + facet_wrap(~reps) + 
  opts(title="Autocorrelation on replicates from a system approaching a crash")
@
\caption{The pattern of autocorrelation in replicate simulations from a simulation of a system which is approaching a saddle node bifurcation.  While a defintitive trend is occassionally visible, clearly we will statistical methods to define what constitutes an "increase."  Our model-based toolset provides this.}\label{crashacor}
\end{center}
\end{figure}
\setkeys{Gin}{width=0.5\textwidth}

@@

\begin{figure}[H]
<<beanplot, fig.width=6>>=
require(beanplot)
beanplot(value ~ simulation, lr, what=c(0,1,0,0))
abline(h=observed, lty=2)
@
\end{figure}

@@

%\subsection{Visualizing the simulation replicates}
%
%The \texttt{reps} list also contains the simulation data from each replicate
%\setkeys{Gin}{width=0.95\textwidth}
%
%\begin{figure}[H]
%<<<repsplot, fig.width=7>>=
%sims <- get_replicates(reps)
%ggplot(sims) + geom_line(aes(time, value, group=rep), alpha=0.1) + facet_wrap(~model)
%@
%\end{figure}
%\setkeys{Gin}{width=0.5\textwidth}

@@

<<moresims>>=
nreps <- 500
Asim <- simulate(A, nreps)
Bsim <- simulate(B, nreps)
@

@@

And gather and plot the distributions,
\begin{figure}[H]
<<tidybean, fig.width=6>>=
tidy <- melt(data.frame(null=wsA$tau, test=wsB$tau))
names(tidy) <- c("simulation", "value")
beanplot(value ~ simulation, tidy, what=c(0,1,0,0))
abline(h=observed, lty=2)
@
\end{figure}

@@

Lastly we save the data from each of these examples for future reference.   
<<saveall>>=
save(list=ls(), file="tutorial.rda")
@
